Supporting Information

### 2015-09-30 ms.Rmd
Add manual list of "interesting" genes in clusters Add SPL/ALOG sections to discussion Reformat legend on sf_pca (fixes #5) Jitter expression (tpm) plots Escape unicode error when exporting to PDF Output SI as tufte pdf?

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    dev: "CairoPDF"
    toc: true
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  pdf_document:
    fig_caption: yes
    number_sections: yes
bibliography: bib/papersLib.bibtex
---

@@

## Rice inflorescence development
### Branching & grain yield
### Sequential changes in meristem activity
### Discuss a few key genes?

@@

@@

@@

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes:
  \usepackage{graphicx}
  \usepackage[utf8]{inputenc}
  \DeclareUnicodeCharacter{2265}{$\geq$}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    dev: "CairoPDF"
    toc: true
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  pdf_document:
    fig_caption: yes
    number_sections: yes
  rmarkdown::tufte_handout:
    default
bibliography: bib/papersLib.bibtex
---

@@

## Rice inflorescence development
## Branching & grain yield
## Sequential changes in meristem activity
## Discuss a few key genes?

@@

Two G1-Like (ALOG) genes, *G1L2* and *G1L5* (*TAWAWA*), were present in clusters `r getClusterName('dec', 'small')` and `r getClusterName('dec', 'dec')` respectively. Only three ALOG genes are expressed in the meristem RNA sequencing dataset, but they share a similar expression pattern (`r I(pasteLabel("Figure ", figCount, "f_alogFamily"))`). *G1L5* mutants **do what, incl. ref**, and the co-expression of other ALOG genes suggests redundancy within the family.

@@

1. Cluster 1
  + FZP
  + WRKY81
  + OsFBX127, OsFBX291
  + MADS5, MADS56
  + BZIP46, BZIP62
  + YAB6
  + LOC_Os07g02800 (MYB family?), LOC_Os07g12910 (PHD protein?)
2. Cluster 2
  + G1L2
  + SPL19
  + MADS47
  + HOX13
  + OsFBX30, OsFBO13, OsFBX258
3. Cluster 3
  + SNB
  + G1L5 (TAWAWA)
  + EP3 (OsFBK5), OsFBX257, OsFBX263, OsFBX333, OsFBX334, OsFBX421
  + MADS57
  + BZIP79
  + ARF9, SAUR25, OsSAUR48
  + WRKY36
  + BC10
  + LOC_Os12g39640 (MYB family?)
4. Cluster 4
  + PLT9 (AP2-like)
  + MADS61
  + ARF6A, OsSAUR33, LOC_Os08g44750 (auxin-induced protein 5NG4)
  + OsFBX18
  + BZIP23
  + ROC1, ROC3, LOC_Os09g35760 (homeobox/START)
5. Cluster 5
  + IDS1, ERF61 (AP2)
  + OsFBX109
  + LOC_Os08g25799 (MYB family?)
6. Cluster 6
  + SPL3, SPL12
  + WRKY123
  + MIR319A (leaf morphology / cold tolerance in indica: 10.1111/pce.12130. Nothing about inflorescence. Strange results, check.)
  + OsFBX14, OsFBL4, OsFBLD1
  + ARF2
  + C3H22
  + LOC_Os04g35430 (PHD domain?)
7. Cluster 7
  + LOGL1, LOGL6
  + BZIP47
  + HOX14
  + WRKY88
  + SHR1
  + SCR (GRAS)
  + NAC41 (No apical meristem protein)
  + OsFBO2, OsFBX125, OsFBX349
  + LOC_Os03g53700 (PHD domain?)
  + LOC_Os08g06240 (MYB domain?)
8. Cluster 8
  + PAP2 (MADS34)
  + DEP1
  + OsFBK1
  + SAUR6
  + LOC_Os02g13310 (homeobox?)

@@

The strong expression of SPL genes (which possess the SBP-box) in the RM and PBM and their presence in clusters `r getClusterName('small', 'dec')` and `r getClusterName('dec', 'small')` suggests involvement in the early stages of inflorescence development. Overexpression of *WEALTHY FARMER'S PANICLE* (*WFP*/*SPL14*), which was detected by *in situ* hybridisation experiments in the RM and branch meristems in wild-type plants, is associated with increased branching and grain yield [@Jiao:2010ft; @Miura:2010it]. *WFP*, *SPL3*, *SPL12* and *SPL17* are all highly expressed in the RM, gradually decrease in expression and have weakest expression in the SM. These genes are all targets of *miR156*, a microRNA that causes reduced panicle size and delayed flowering when overexpressed (**ref: http://www.ncbi.nlm.nih.gov/pmc/articles/PMC1557610/**).

### 2015-09-30 si.Rmd
Add manual list of "interesting" genes in clusters Add SPL/ALOG sections to discussion Reformat legend on sf_pca (fixes #5) Jitter expression (tpm) plots Escape unicode error when exporting to PDF Output SI as tufte pdf?

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    dev: "CairoPDF"
  pdf_document:
    fig_caption: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
bibliography: bib/papersLib.bibtex
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("png", "cairo_pdf"),
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               fig.height = 3.150,
               fig.width = 3.150,
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

pander::panderOptions("table.caption.prefix", "")

source('src/R/figures.R')

@@

``` {r st_libStats, results = "asis"}
pander::set.caption(paste0(
  I(pasteLabel("**Table S", s_tableCount, "st_libStats")),
  "**: Library and sequencing statistics."))
pander::pandoc.table(st_libStats, split.tables = Inf, missing = "", round = 1, emphasize.strong.cols = 1,
                     justify = c("right", rep("center", length(names(st_libStats)) - 1)))
```

@@

```{r sf_pca}
print(sf_pca)
```

>>>>

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes:
  \usepackage{graphicx}
  \usepackage{caption}
  \captionsetup[figure]{labelfont=bf}
  \renewcommand{\thefigure}{S\arabic{figure}}
output:
  rmarkdown::tufte_handout:
    dev: "CairoPDF"
  pdf_document:
    fig_caption: yes
    number_sections: yes
    dev: "CairoPDF"
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
bibliography: bib/papersLib.bibtex
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
#               fig.align = 'center', 
               dev = "cairo_pdf",
               dpi=300,
               fig.show='hold',
               fig.height = 3.150,
               fig.width = 3.150,
               out.width = 3.150,
               out.height = 3.150,
#               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

pander::panderOptions("table.caption.prefix", "")
source('src/R/figures.R')

@@

``` {r st_libStats, results = "asis", fig.cap = I(pasteLabel("**Table S", s_tableCount, "st_libStats"))}
pander::set.caption(paste0(
  I(pasteLabel("**Table S", s_tableCount, "st_libStats")),
  "**: Library and sequencing statistics."))
pander::pandoc.table(st_libStats, split.tables = Inf, missing = "", round = 1, emphasize.strong.cols = 1,
                     justify = c("right", rep("center", length(names(st_libStats)) - 1)))
```

@@

```{r sf_pca, fig.cap = paste0("Principal components analysis of transformed read counts for each library. The two libraries made from degraded RNA did not cluster with other libraries (see ", I(pasteLabel("Table S", s_tableCount, "st_libStats")), "), suggesting that the use of degraded RNA affected quantification of expression. For this reason these two libraries were not included in subsequent analyses.")}
print(sf_pca)
```
